### 2023-10-05 1.Introduction/motivation.tex
Improved motivation

\acp{AI} are very power hungry algorithms which limits its use in embedded systems and power efficient devices.
Furthermore, the time an \ac{AI} takes to compute its output can become quite long. So much so that the most complex ones only run on online and very powerful servers, like the aforementioned \textit{ChatGPT}.

@@

>>>>

\acp{AI} are very power hungry algorithms which limits its use in embedded systems and power efficient devices.
Furthermore, the time an \ac{AI} takes to compute its output quickly rises, especially on lower end chip such as the ones used in embedded systems. So much so that the most complex ones only run on online and very powerful servers, like the aforementioned \textit{ChatGPT}.

@@

Somre research \cite{celegans}, focuses on reproducing parts of the nervous system of a small organism. This could be applied on larger organisms, or, in the long term, reproduce part of the human brain. Using analog computers, small chips could be used to replace a part of one's brain non functionnal part.
